### 2020-08-21 v0.2.1/assets/NetworkModel/network.tex
build based on 41ea9c6

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\large}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = 0.25cm, nodes={anchor=center}]{
             \& \draw pic (kaynak2) {Component={Source II}}; \& \&   \\[-1cm]
            \draw pic (kaynak1) {Component={Source I}};    \& \& \draw pic (statiksistem1) {Component={StaticSystem I}}; \& \draw pic (statiksistem2) {Component={StaticSystem II}}; \\
            \draw pic (kutuk1) {Component={Sink I}}; \& \& \& \draw pic (kutuk2) {Component={Sink II}}; \\
        };
        % Glow the blocks
        \foreach \x in {kaynak1, kaynak2, kutuk1, kutuk2, statiksistem1, statiksistem2}{
            \drawshadowbis{\x-edge};
        }
        % Draw connections 
        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
            \draw[-] (kaynak1-edge.east) -- ++(0.75cm, 0cm) coordinate(a);
            \draw[->] ([yshift=1mm] a) |- (kutuk1-edge.east);
            \draw[->] (a) |- ([yshift=-0.25cm] statiksistem1-edge.west);
            \draw[-] (kaynak2-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
            \draw[->] ([yshift=1mm] b) |- ([yshift=0.25cm] statiksistem1-edge.west);
            \draw[->] (statiksistem1-edge.east) |- (statiksistem2-edge.west);
            \draw[-] (statiksistem2-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
            \draw[->] ([yshift=1mm] c) |- (kutuk2-edge.east);
        \end{scope}

        % Draw rectangle for subsystem 
        \draw[thick, dashed] ([xshift=-0.25cm, yshift=0.25cm] kaynak2-edge.north west) rectangle ([xshift=0.25cm, yshift=-0.75cm] statiksistem2-edge.south east);
        \draw (statiksistem2-edge.north west) node[yshift=1.75cm, xshift=1cm]{SubSystem};

        % \Place clock 
        \begin{scope}[shift={(-5.75cm, -4.5cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.75*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=0.5*\mw, yshift=1.5*\mh] statiksistem2-edge.north east);
        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=6*\mw]{Model};
    \end{tikzpicture}
\end{document}

>>>>

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = -0.75cm, nodes={anchor=center}]{
            \draw pic (ds1) {Component={ODESystem $1$}}; \& \& \draw pic (ss1) {Component={StaticSystem $1$}}; \\
            \draw node[]{\huge $\vdots$}; \& \draw pic (ss0) {Component={StaticSystem $0$}}; \& \draw[ultra thick] node[]{\huge $\vdots$}; \\
            \draw pic (dsn) {Component={ODESystem $n$}}; \& \& \draw pic (ssn) {Component={Static\\System $n$}}; \\[1.5cm]
             \& \draw pic (kutuk) {Component={Sink}}; \& \\
        };
        % Glow the blocks
        \foreach \x in {ds1, dsn, ss0, ss1, ssn, kutuk}{
            \drawshadowbis{\x-edge};
        }
        % Draw connections 
        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
            \draw[-] (ds1-edge.east) -- ++(1cm, 0cm) coordinate(a);
            \draw[-] (dsn-edge.east) -- ++(1cm, 0cm) coordinate(b);
            \draw[->] ([yshift=1mm] a) |- ([yshift=0.5cm] ss0-edge.west);
            \draw[->] ([yshift=-1mm] b) |- ([yshift=-0.5cm] ss0-edge.west);
            \draw (ss0-edge.west) node [xshift=-0.75cm]{\huge $\vdots$};
            \draw (ss0-edge.east) node [xshift=0.75cm]{\huge $\vdots$};
            \draw[-] ([yshift=0.5cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(c);
            \draw[-] ([yshift=-0.5cm] ss0-edge.east) -- ++(0.5cm, 0cm) coordinate(d);
            \draw[->] ([yshift=-1mm] c) |- (ss1-edge.west);
            \draw[->] ([yshift=1mm] d) |- (ssn-edge.west);
            \draw[-] (ds1-edge.east) -- ++(0.75cm, 0cm) coordinate(e);
            \draw[-] (dsn-edge.east) -- ++(0.25cm, 0cm) coordinate(f);
            \draw[->] (e) |- ([yshift=0.5cm] kutuk-edge.west);
            \draw[->] (f) |- ([yshift=-0.5cm] kutuk-edge.west);
            \draw (kutuk-edge.west) node [xshift=-0.75cm]{\huge $\vdots$};
            \draw[->] ([xshift=-1cm] ds1-edge.west) node[anchor=east]{$u_1$} -- (ds1-edge.west);
            \draw[->] ([xshift=-1cm] dsn-edge.west) node[anchor=east]{$u_n$} -- (dsn-edge.west);
            \draw[->] (ss1-edge.east) -- ([xshift=1cm] ss1-edge.east) node[anchor=west]{$u_1$};
            \draw[->] (ssn-edge.east) -- ([xshift=1cm] ssn-edge.east) node[anchor=west]{$u_n$};
        \end{scope}

        % Draw rectangle for network
        \draw[thick, dashed] ([xshift=-1.75cm, yshift=0.25cm] ds1-edge.north west) rectangle ([xshift=1.75cm, yshift=-1.25cm] ssn-edge.south east);
        \draw (ssn-edge.south) node[yshift=-1cm, xshift=1.7cm]{SubSystem};

        % \Place clock 
        \begin{scope}[shift={(-5.75cm, -5cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.5*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=1*\mw, yshift=0.5*\mh] ss1-edge.north east);
        \draw (clk-clockedge.east) node[yshift=0*\mh, xshift=5.75*\mw]{Model};
    \end{tikzpicture}
\end{document}

### 2020-08-21 v0.2.1/assets/Subsystem/subsystem.tex
build based on 41ea9c6

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [
            matrix of nodes, 
            ampersand replacement=\&, 
            column sep = 1cm, 
            row sep = 0.5cm, 
            nodes={
                text height=1.5ex,
                text depth=.25ex,
                anchor=center}
                ]{
                     \& \draw pic (writerin) {Component={writerin}}; \& \& \&  \\
                     \draw pic (gen) {Component={gen}}; \& \draw pic (adder) {Component={adder}}; \& \& \draw pic (gain) {Component={gain}}; \& \draw pic (writerout) {Component={writerout}}; \\
                     \& \& \draw pic (memory) {Component={Memory}}; \& \&  \\
                };

        % Draw connections 
        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
            \def\shiftamount{0.5mm};
            \draw[->] (gen-edge.east) -- node[midway, anchor=north]{$r(t)$} (adder-edge.west);
            \draw[->] (adder-edge.east) -- node[midway, anchor=north]{$u(t)$} (gain-edge.west);
            \draw[->] (gain-edge.east) -- (writerout-edge.west);
            \draw[->] (gain-edge.east) -- (writerout-edge.west);
            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
            \draw[->] ([yshift=0.75mm] a) |- node[midway, xshift=-1cm, anchor=north]{$y(t)$} (memory-edge.east);
            \draw[->] (memory-edge.west) -| node[midway, xshift=1cm, anchor=north]{$\hat{y}(t)$} (adder-edge.south);
            \draw[-] (gen-edge.east) -- ++(0.5cm, 0cm) coordinate(b);
            \draw[->] (b) |- (writerin-edge.west);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-5cm, -3cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] (-6, -4) rectangle (6, 2.5);
        \draw (0,0) node[xshift=4.75cm, yshift=-3cm]{Model};
    \end{tikzpicture}
\end{document}

>>>>

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [
            matrix of nodes, 
            ampersand replacement=\&, 
            column sep = 1cm, 
            row sep = 0.5cm, 
            nodes={
                text height=1.5ex,
                text depth=.25ex,
                anchor=center}
                ]{
                    \& \draw pic (adder) {Component={adder}}; \& \draw pic (gain) {Component={gain}}; \\
                    \draw pic (gen) {Component={gen}}; \&  \&  \\
                };

        % Draw connections 
        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
            \def\shiftamount{0.5mm};
            \draw[->] (gen-edge.east) -| (adder-edge.south);
            \draw[->] (adder-edge.east) -- (gain-edge.west);
            \draw[->] ([xshift=-3.5cm] adder-edge.west) -- (adder-edge.west);
            \draw[->] (gain-edge.east) -- ++(2cm, 0cm);
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] (-3.5, -2) rectangle (4, 1.5);
        \draw (0,0) node[yshift=-1.5cm, xshift=3.5cm]{sub};
    \end{tikzpicture}
\end{document}
